\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 experience.tex
CScale text.

Fabric services have a lot of asynchrony, which make them interesting targets for systematic testing with \psharp{}.
Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
The system that we wished to test is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
Prior work~\cite{deligiannis2015psharp}
created a model of Fabric with limited functionality;
it used a mixture of \csharp{} and \psharp{} internally,
only supported one in-flight replication request
(which restricts the asynchrony that can be tested),
and only supported one Fabric service.
Our new Fabric model was re-written to use only \psharp{}
internally,
support an arbitrary number of Fabric services and in-flight replication requests,
and in general be a more complete model of Fabric.
Note that \csharp{} code is still required to interface with the existing
\csharp{} service code.
We refer to our \csharp{} code
as the \emph{translation layer}
and
 the user-written \csharp{} service code as \emph{user code}.

@@

\subsubsection{CScale}

>>>>

Fabric services have a lot of asynchrony, which make them interesting targets for systematic testing with \psharp{}.
Our primary goal was to create a \psharp{} model of Fabric to allow
thorough testing of services, where Fabric's asynchrony is controlled 
by the \psharp{} runtime.
Prior work~\cite{deligiannis2015psharp}
created a model of Fabric with limited functionality;
it used a mixture of \csharp{} and \psharp{} internally,
only supported one in-flight replication request
(which restricts the asynchrony that can be tested),
and only supported one Fabric service.
Our new Fabric model was re-written to use only \psharp{}
internally,
support an arbitrary number of Fabric services and in-flight replication requests,
and in general be a more complete model of Fabric.
Note that \csharp{} code is still required to interface with the existing
\csharp{} service code.
We refer to our \csharp{} code
as the \emph{translation layer}
and
 the user-written \csharp{} service code as \emph{user code}.

@@

\subsubsection{CScale}
The system that we wished to test is \emph{CScale}~\cite{X},
a big data-stream processing system that chains multiple Fabric services
in a directed acyclic graph.
A key challenge is that
CScale contains inter-service communication
that resolves services
via Fabric but communicates
using a non-Fabric remote procedure call protocol.
In order to close the system,
we first implemented service resolution in our Fabric model,
which resolves Fabric service names to IP addresses.
We then replaced the inter-service communication
classes in CScale with our own;
our replacement includes the ability to map
URLs to \psharp{} machines
so that remote procedure calls are now implemented
by sending and receiving \psharp{} events.
Thus,
we converted a multi-process system
that runs on the Fabric platform
and 
uses network communication
into 
a single process system that uses multiple threads,
contains
the Fabric model
and the CScale services,
and does not use network communication.
Additional changes were needed to
remove certain static (per-process) fields,
as these were inadvertently
being shared between services
after making the system a single process.

A key challenge in our work
was to test CScale despite the fact that it
uses various synchronous and asynchronous APIs
other than \psharp{}.
This work is still in-progress.
However,
we were able to find a \texttt{NullReferenceException}
bug
in CScale
by running it on our model.
